### 2017-08-28 paper/intro.tex
Added some content related to test flakiness

The dimensions of analysis we considered in this study are (i)
feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practitioners to
the technology and to understand their reasons.  The dimension
\emph{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{tradeoffs} considers the problems in running tests in parallel,
including test flakiness~\cite{luo-etal-fse2014}.  We briefly
summarize our findings in the following.

>>>>

The dimensions of analysis we considered in this study are (i)
feasibility, (ii) adoption, (iii) speedup, and (iv) tradeoffs.  The
dimension \emph{feasibility} measures the potential of parallelization
to reduce testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
execution cost was dominated by a single test case in the suite.  The
dimension \emph{adoption} evaluates how often existing open-source
projects use parallelization schemes and how developers involved in
costly projects (not using test suite parallelization) perceive this
technology.  It is important to measure resistance of practitioners to
the technology and to understand their reasons.  The dimension
\emph{speedups} evaluates the observed impact of
parallelization\Comment{~---~when used in selected open-source
  projects~---~} in running times.  Finally, the dimension
\emph{tradeoffs} considers the problems in running tests in parallel.
\Jbc{
In practice, some test suites may not be prepared for a multithreaded
execution.
For instance, developers may unconsciously create tests assuming an
specific order of execution.
While parallelism may speed up tests, in those cases,
tests may yield non-deterministic results due to data races.
In general, a test that either pass or fail under the same conditions
is known as a ``flaky test''~\cite{luo-etal-fse2014}. It is important
to measure the presence of test flakiness and the trade-offs to
overcome this issue.}
We briefly summarize our findings in the following.
